Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-31 article/index.Rmd
fixed titles of region sections in discussion

# allow easy dynamic value integration
sf_prep <- "sf_prep.txt"
sf_desc <- "sf_desc.txt"
r <- txtstorage::read
a <- function(x) {r("regions graves amounts", sf_prep) %>% strsplit(", ") %>% unlist %>% magrittr::extract(grepl(x, .))}
```

>>>>

# allow easy dynamic value integration
sf_prep <- "sf_prep.txt"
sf_desc <- "sf_desc.txt"
r <- txtstorage::read
a <- function(x) {r("regions graves amounts", sf_desc) %>% strsplit(", ") %>% unlist %>% magrittr::extract(grepl(x, .))}
```
